Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
minor edit

To implement the integration on $\Ball{R}{\vx} \cap \Shape$
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all
digital points inside such domain (Fig.~\ref{fig:approx}-$b$) and then
to estimate the geometrical moment as the sum of the geometrical
moments of each elementary cubes lying in the intersection. On GPU,
\emph{mipmap} textures are used to obtain a multi-resolution information: if the
input binary object is stored in a 3D texture, GPU hardware can
construct a multi-resolution pyramid such that 8 neighboring voxel
intensities at level $l$ are averaged to define the voxel value at
level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$
belonging to the cube of center $(x,y,z)$ and edge length $2^l$. As a
consequence, we can approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by
considering mipmap values at a given resolution $l$
(Fig.~\ref{fig:approx}-$c$). In this case, errors only occurs for
cells lying inside $\Shape$ (with density 1) not entirely covered by
$\Ball{R}{\vx}$. Furthermore, \emph{mipmap} textures give us a fast method to know if a voxel is inside $\Shape$, for all levels. Indeed, if the mipmap value is greater than $0.5$, the voxel associated is \emph{at least} half inside $\Shape$.
\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    gray values) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}

>>>>

To implement the integration on $\Ball{R}{\vx} \cap \Shape$
(Fig.~\ref{fig:approx}-$a$), a naive approach consists in scanning all digital
points inside such domain (Fig.~\ref{fig:approx}-$b$) and then to estimate the
geometrical moment as the sum of the geometrical moments of each elementary
cubes lying in the intersection. On GPU, \emph{mipmap} textures are used to
obtain a multi-resolution information: if the input binary object is stored in a
3D texture, GPU hardware can construct a multi-resolution pyramid such that 8
neighboring voxel intensities at level $l$ are averaged to define the voxel
value at level $l+1$. If the level 0 corresponds to the binary input object, at
a given level $l$, a voxel $(x,y,z)$ contains the fraction of $\DSh$ belonging
to the cube of center $(x,y,z)$ and edge length $2^l$. As a consequence, we can
approximate the volume of $\Ball{R}{\vx}\cap\Shape$ by considering mipmap values
at a given resolution $l$ (Fig.~\ref{fig:approx}-$c$). In this case, errors only
occurs for cells lying inside $\Shape$ (with density 1) not entirely covered by
$\Ball{R}{\vx}$. Furthermore, the \emph{mipmap} texture can be used to design,
using a single texture probe, a fast inclusion test of a given cell $c$ at level
$l$ into the shapes: we say that $c$ is in $\Shape$ if its density (retrieved
from the texture probe at level l) is greater than $1/2$. The idea here is to
mimic a lend of adaptive Gauss digitization process.

\begin{figure}
  \begin{center}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-1}}
    \subfigure[]{\includegraphics[width=4cm]{figs/approx-reg-2}}
  \end{center}
  \caption{Integral computation with an area estimation from pixel
    counting $(b)$ or from densities (represented by different
    gray values) in a mipmap approximation of $\Shape$.}
  \label{fig:approx}
\end{figure}
